Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-18 prop_letter.tex
prop.bib @Article{Appleby_2005} Added...

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{Peres2003,BarrettKent2004}.  For example,
Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the Kochen-Specker
theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion
continues on whether contextuality is experimentally
verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
fundamental question is how to make mathematical theories of quantum
mechanics that are intrinsically, rather than only implicitly,
consistent with the resources available for the realistic accuracy of
an actual measurement.

>>>>

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}.  For example,
Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the Kochen-Specker
theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion
continues on whether contextuality is experimentally
verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
fundamental question is how to make mathematical theories of quantum
mechanics that are intrinsically, rather than only implicitly,
consistent with the resources available for the realistic accuracy of
an actual measurement.
